Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-07-30 nir_companions.tex
Update on Overleaf.

Due to the poorly separated observation times relative to the long orbital periods, this method was revealed to be inappropriate for these observations as the RV separation of the companion spectra between observations (\(\le 2.3\)\kmps{}) is significantly smaller than the FWHM (full width half maximum) of individual spectral lines (\(\sim\)6\kmps at \(\rm R=50\,000\)).  The small separation of the companion causes the lines of the companion to also mutually cancel, severely reducing the residual signal to well below the available noise level. The requirement of well separated RVs for the companion spectra was clearly stated in the original proposal but was not satisfied when the observations were obtained\footnote{see Sect.~\ref{subsubsec:differential scedualing} for more details}. {\rd The very large orbital periods of some of the targets would not produce a sufficient RV signal during one semester. This was a possible oversight during the proposal stage.} The largest estimated companion \(\Delta RV\) separation between the observations of each target is provided in the seventh column of Table~\ref{tab:estimatedparameters}. Radial velocity constraints are also valid for other studies such as the detection of reflected light from exoplanets~\cite{martins_evidence_2015}.

@@

{\rd BIC FOR HD211847###########}

@@

\subsubsection{Differential scheduling challenges}
\label{subsubsec:differential scedualing}
This work has revealed that more care needs to be taken in planning the observations for the spectral differential analysis of faint companions in the future. Paying attention in particular to the FWHM of the lines in the region (governed by resolution and wavelength); the estimated companion \(\Delta RV \); the previous observations from different observing periods; and keeping consistent detector settings.

>>>>

Due to the poorly separated observation times relative to the long orbital periods, this method was revealed to be inappropriate for these observations as the RV separation of the companion spectra between observations (\(\le 2.3\)\kmps{}) is significantly smaller than the FWHM (full width half maximum) of individual spectral lines (\(\sim\)6\kmps at \(\rm R=50\,000\)).  The small separation of the companion causes the lines of the companion to also mutually cancel, severely reducing the residual signal to well below the available noise level. The requirement of well separated RVs for the companion spectra was clearly stated in the original proposal but was not satisfied when the observations were obtained\footnote{see Sect.~\ref{subsubsec:differential-schedualing} for more details}. {\rd The very large orbital periods of some of the targets would not produce a sufficient RV signal during one semester. This was a possible oversight during the proposal stage.} The largest estimated companion \(\Delta RV\) separation between the observations of each target is provided in the seventh column of Table~\ref{tab:estimatedparameters}. Radial velocity constraints are also valid for other studies such as the detection of reflected light from exoplanets~\cite{martins_evidence_2015}.

@@

{\rd BIC FOR HD211847\#\#\#\#\#\#\#\#\#\#\#}

@@

\subsubsection{Differential scheduling challenges}
\label{subsubsec:differential-schedualing}
This work has revealed that more care needs to be taken in planning the observations for the spectral differential analysis of faint companions in the future. Paying attention in particular to the FWHM of the lines in the region (governed by resolution and wavelength); the estimated companion \(\Delta RV \); the previous observations from different observing periods; and keeping consistent detector settings.
